Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?

### 2018-09-17 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update paper

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au"
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different from the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard and then one of Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government. However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.

@@

The formatting of the Hansard records changes between the different parliaments and over time. We use R scripts to convert the PDFs into daily text records.[^seeMyScripts] These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018. The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014. Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are fixed when they occur at scale and can be identified.

@@

## Parliamentary meta data

TALK ABOUT THE ADDITIONAL DATA

In general,

## Topic pre-processing
There is much more on topic modelling in the next section because topics are the main data analysed in this paper, but here we briefly discuss the pre-processing steps  of creating the topics.

records, and clean the records using functions from the \texttt{Tidyverse} R package of @Wickham2017, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS]. The result is a

# Model
The primary model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{STM} R package of @RobertsStewartAiroldiRPackage. The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent. In this section a brief overview of both the LDA model and the STM approach is provided and then the specifics of how we consider events in this setting are discussed.

## Latent Dirichlet Allocation
Each day's Hansard record needs to be classified by its topic. Sometimes Hansard includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods. One way to get consistent estimates of the topics of each statement in Hansard is to use the latent Dirichlet allocation (LDA) method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.

The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then chooses words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics. The topics are not specified *ex ante*; they are an outcome of the method. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. This provides more flexibility than other approaches such as a strict word count method. The goal is to have the words found in each day's Hansard group themselves to define topics.

As applied to Hansard, the LDA method considers each statement to be a result of a process where a politician first chooses the topics they want to speak about. After choosing the topics, the speaker then chooses appropriate words to use for each of those topics.

More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics. For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).

```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics"}
document_1 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
  )

document_2 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.01, 0.04, 0.35, 0.20, 0.4)
  )

# par(mfrow=c(2,1))
ggplot(document_1, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 1") +
  coord_cartesian(ylim = c(0, 0.4))
ggplot(document_2, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

@@

```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'}
topic_1 <- tibble(
  Terms = c(
  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
  ),
  Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2)
  )

topic_2 <- tibble(
  Terms = c(
  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
  ),
  Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)
  )

# par(mar = c(4, 4, 0.1, 0.1))
ggplot(topic_1, aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over terms for Topic 1") +
  coord_cartesian(ylim = c(0, 0.4))
ggplot(topic_2, aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over terms for Topic 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

>>>>

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard and then one of Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government. However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.

@@

The formatting of the Hansard records changes between the different parliaments and over time. We use R scripts to convert the PDFs into daily text records.[^seeMyScripts] These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018. The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014. Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are fixed when they occur at scale and can be identified. The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.

@@

Text usually needs to be pre-processed before topic models can be used. The specific steps that we take are to remove numbers and punctuation and to change all the words to lower case. Then the sentences are deconstructed and each word considered individually. In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.

## Additional information
Data from other sources are useful to complement the parliamentary text data. For instance, although the name, party, and division represented are contained in Hansard records they are inconsistent. Also non-Hansard information about the politicians can inform the analysis. This includes: date of birth and date of death; sex; date of entry to parliament and exit from parliament; some aspects of their pre- and post-parliamentary career; some aspects of their parliamentary career, such as ministry appointments; and electoral information such as primary and two-party-preferred results.

The main sources for this additional supplementary information are the handbooks supplied by the various parliaments (Table 2).

| Parliament  | House  | Source |
|:------|-----:|---------:|
| Commonwealth      | House of Representatives | Parliamentary Handbok |
|                   | Senate                   | **[TBD]** |
| Queensland        | Legislative Assembly     |  **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| New South Wales   | Legislative Assembly     | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| Victoria          | Legislative Assembly     | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| Tasmania          | House of Assembly        | **[TBD]** |
|                   | Legislative Council      |  **[TBD]** |
| South Australia   | House of Assembly        | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |
| Western Australia | Legislative Assembly     | **[TBD]** |
|                   | Legislative Council      | **[TBD]** |

The additional information from the handbooks had many errors and it was supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData]

[^seeMyAdditionalData]: An example of the additional information is provided in the Appendix. The datasets are available on request.

# Model
The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage. The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent. In this section a brief overview of both the LDA model and the STM approach is provided and then the specifics of how we consider events in this setting are discussed.

## Latent Dirichlet Allocation
When the text data is being modelled at the day level then each day's Hansard record needs to be classified by its topic. Although more- or less-fine levels of analysis are possible. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods. One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.

The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics. The topics are not specified *ex ante*; they are an outcome of the method. In this sense, this approach can be considered unsupervised machine learning. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. This provides more flexibility than other approaches such as a strict word count method. The goal is to have the words found in each day's Hansard group themselves to define topics.

As applied to Hansard, the LDA method considers each statement to be a result of a process where a politician first chooses the topics they want to speak about. After choosing the topics, the speaker then chooses appropriate words to use for each of those topics. More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics. For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).

```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 3}
tibble(
  Topics = rep(c("1", "2", "3", "4", "5"), 2),
  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
  document = c(rep("Document 1", 5), rep("Document 2", 5))
  ) %>%
  ggplot(aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  facet_wrap(vars(document), ncol = 2, scales = "free") +
  theme(strip.background = element_blank()) + 
  coord_flip()

```

@@

```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 3}
tibble(
  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
  ) %>%
  ggplot(aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  facet_wrap(vars(Topics), ncol = 2, scales = "free") +
  theme(strip.background = element_blank()) + 
  coord_flip()

```

### 2018-09-17 outputs/docs/events/svm-rmarkdown-article-example.tex
Update paper

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 16, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }

@@

\begin{document}

@@

New governments often go to some trouble to be different from the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by John Howard and then one of
Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
significant events such as the 9/11 attacks or the Great Recession have
often altered the course of a government. However it is not so clear
which events drive changes, for how long these changes persist, and what
was given up due to the change.

@@

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in the Appendix. The full set of
  scripts are available on request.} These scripts are primarily based
on: the \texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified.

@@

\subsection{Parliamentary meta data}\label{parliamentary-meta-data}

TALK ABOUT THE ADDITIONAL DATA

In general,

\subsection{Topic pre-processing}\label{topic-pre-processing}

There is much more on topic modelling in the next section because topics
are the main data analysed in this paper, but here we briefly discuss
the pre-processing steps of creating the topics.

records, and clean the records using functions from the
\texttt{Tidyverse} R package of \citet{Wickham2017}, the
\texttt{Tidytext} R package of \citet{SilgeRobinson2016} and the
{[}INSERT OTHERS{]}. The result is a

@@

The primary model that we use in this paper is the Structural Topic
Model (STM) as implemented by the \texttt{STM} R package of
\citet{RobertsStewartAiroldiRPackage}. The basis of this type of topic
modelling is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section a brief overview of both the LDA
model and the STM approach is provided and then the specifics of how we
consider events in this setting are discussed.

@@

Each day's Hansard record needs to be classified by its topic. Sometimes
Hansard includes titles that make the topic clear. But not every
statement has a title and the titles do not always define topics in a
well-defined and consistent way, especially over longer time periods.
One way to get consistent estimates of the topics of each statement in
Hansard is to use the latent Dirichlet allocation (LDA) method of
\citet{Blei2003latent}, for instance as implemented by the R package
`topicmodels' by \citet{Grun2011}.

The key assumption behind the LDA method is that each day's text, `a
document', in Hansard is made by speakers who decide the topics they
would like to talk about in that document, and then chooses words,
`terms', that are appropriate to those topics. A topic could be thought
of as a collection of terms, and a document as a collection of topics.
The topics are not specified \emph{ex ante}; they are an outcome of the
method. Terms are not necessarily unique to a particular topic, and a
document could be about more than one topic. This provides more
flexibility than other approaches such as a strict word count method.
The goal is to have the words found in each day's Hansard group
themselves to define topics.

As applied to Hansard, the LDA method considers each statement to be a
result of a process where a politician first chooses the topics they
want to speak about. After choosing the topics, the speaker then chooses
appropriate words to use for each of those topics.

More generally, the LDA topic model works by considering each document
as having been generated by some probability distribution over topics.
For instance, if there were five topics and two documents, then the
first document may be comprised mostly of the first few topics; the
other document may be mostly about the final few topics (Figure
@ref(fig:topicsoverdocuments)).

\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-1.pdf}
\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-2.pdf}

Similarly, each topic could be considered a probability distribution
over terms. To choose the terms used in each document the speaker picks
terms from each topic in the appropriate proportion. For instance, if
there were ten terms, then one topic could be defined by giving more
weight to terms related to immigration; and some other topic may give
more weight to terms related to the economy (Figure
@ref(fig:topicsoverterms)).

\begin{figure}
\includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1} \includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-2} \caption{Probability distributions over terms}\label{fig:topicsoverterms}
\end{figure}

@@

After the documents are created, they are all that we have to analyse.
The term usage in each document, \(w_{1:D, 1:N}\), is observed, but the
topics are hidden, or `latent'. We do not know the topics of each
document, nor how terms defined the topics. That is, we do not know the
probability distributions of Figures @ref(fig:topicsoverdocuments) or
@ref(fig:topicsoverterms). In a sense we are trying to reverse the
document generation process -- we have the terms and we would like to
discover the topics.

@@

The initial practical step when implementing LDA given a collection of
documents is to remove `stop words'. These are words that are common,
but that don't typically help to define topics. There is a general list
of stop words such as: ``a''; ``a's''; ``able''; ``about'';
``above''\ldots{} An additional list of words that are commonly found in
Hansard, but likely don't help define topics is added to the general
list. These additions include words such as: ``act''; ``amendment'';
``amount''; ``australia''; ``australian''; ``bill''\ldots{} A full list
can be found in Appendix @ref(hansard-stop-word). We also remove
punctuation and capitalisation. The documents need to then be
transformed into a document-term-matrix. This is essentially a table
with a column of the number of times each term appears in each document.

>>>>

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
suggestions. \textbf{Version as of}: September 16, 2018;
\textbf{Comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

@@

New governments often go to some trouble to be different to the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was not supported by John Howard and then one of
Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
significant events such as the 9/11 attacks or the Great Recession have
often altered the course of a government. However it is not so clear
which events drive changes, for how long these changes persist, and what
was given up due to the change.

@@

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in the Appendix. The full set of
  scripts are available on request.} These scripts are primarily based
on: the \texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified. The \texttt{hunspell} package of
\citet{Ooms2017} is also used to help find spelling issues.

@@

Text usually needs to be pre-processed before topic models can be used.
The specific steps that we take are to remove numbers and punctuation
and to change all the words to lower case. Then the sentences are
deconstructed and each word considered individually. In addition to the
packages already mentioned, in this step the R scripts to do this use
the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.

\subsection{Additional information}\label{additional-information}

Data from other sources are useful to complement the parliamentary text
data. For instance, although the name, party, and division represented
are contained in Hansard records they are inconsistent. Also non-Hansard
information about the politicians can inform the analysis. This
includes: date of birth and date of death; sex; date of entry to
parliament and exit from parliament; some aspects of their pre- and
post-parliamentary career; some aspects of their parliamentary career,
such as ministry appointments; and electoral information such as primary
and two-party-preferred results.

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments (Table 2).

\begin{longtable}[]{@{}lrr@{}}
\toprule
Parliament & House & Source\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & Parliamentary
Handbok\tabularnewline
& Senate & \textbf{{[}TBD{]}}\tabularnewline
Queensland & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
New South Wales & Legislative Assembly &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
Victoria & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
Tasmania & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
South Australia & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
Western Australia & Legislative Assembly &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
\bottomrule
\end{longtable}

The additional information from the handbooks had many errors and it was
supplemented by data from the Australian Dictionary of Biography and
Wikipedia.\footnote{An example of the additional information is provided
  in the Appendix. The datasets are available on request.}

@@

The main model that we use in this paper is the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. The basis of this type of topic
modelling is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section a brief overview of both the LDA
model and the STM approach is provided and then the specifics of how we
consider events in this setting are discussed.

@@

When the text data is being modelled at the day level then each day's
Hansard record needs to be classified by its topic. Although more- or
less-fine levels of analysis are possible. Sometimes Hansard records
includes titles that make the topic clear. But not every statement has a
title and the titles do not always define topics in a well-defined and
consistent way, especially over longer time periods. One way to get
consistent estimates of the topics discussed in Hansard is to use the
LDA method of \citet{Blei2003latent}, for instance as implemented by the
R package `topicmodels' by \citet{Grun2011}.

The key assumption behind the LDA method is that each day's text, `a
document', in Hansard is made by speakers who decide the topics they
would like to talk about in that document, and then choose words,
`terms', that are appropriate to those topics. A topic could be thought
of as a collection of terms, and a document as a collection of topics.
The topics are not specified \emph{ex ante}; they are an outcome of the
method. In this sense, this approach can be considered unsupervised
machine learning. Terms are not necessarily unique to a particular
topic, and a document could be about more than one topic. This provides
more flexibility than other approaches such as a strict word count
method. The goal is to have the words found in each day's Hansard group
themselves to define topics.

As applied to Hansard, the LDA method considers each statement to be a
result of a process where a politician first chooses the topics they
want to speak about. After choosing the topics, the speaker then chooses
appropriate words to use for each of those topics. More generally, the
LDA topic model works by considering each document as having been
generated by some probability distribution over topics. For instance, if
there were five topics and two documents, then the first document may be
comprised mostly of the first few topics; the other document may be
mostly about the final few topics (Figure
\ref{fig:topicsoverdocuments}).

\begin{figure}
\centering
\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-1.pdf}
\caption{\label{fig:topicsoverdocuments}Probability distributions over
topics for two documents}
\end{figure}

Similarly, each topic could be considered a probability distribution
over terms. To choose the terms used in each document the speaker picks
terms from each topic in the appropriate proportion. For instance, if
there were ten terms, then one topic could be defined by giving more
weight to terms related to immigration; and some other topic may give
more weight to terms related to the economy (Figure
\ref{fig:topicsoverterms}).

\begin{figure}
\centering
\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1.pdf}
\caption{\label{fig:topicsoverterms}Probability distributions over terms}
\end{figure}

@@

After the documents are created, they are all that we have to analyse.
The term usage in each document, \(w_{1:D, 1:N}\), is observed, but the
topics are hidden, or `latent'. We do not know the topics of each
document, nor how terms defined the topics. That is, we do not know the
probability distributions of Figures \ref{fig:topicsoverdocuments} or
\ref{fig:topicsoverterms}. In a sense we are trying to reverse the
document generation process -- we have the terms and we would like to
discover the topics.

@@

The initial practical step when implementing LDA given a collection of
documents is to remove `stop words'. These are words that are common,
but that don't typically help to define topics. There is a general list
of stop words such as: ``a''; ``a's''; ``able''; ``about'';
``above''\ldots{} An additional list of words that are commonly found in
Hansard, but likely don't help define topics is added to the general
list. These additions include words such as: ``act''; ``amendment'';
``amount''; ``australia''; ``australian''; ``bill''\ldots{} A full list
can be found in Appendix \ref{hansard-stop-word}. We also remove
punctuation and capitalisation. The documents need to then be
transformed into a document-term-matrix. This is essentially a table
with a column of the number of times each term appears in each document.
